%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Top Hat Inc} % Organization
    {Full Stack Web Software Engineer} % Job title
    {Toronto ON, Canada} % Location
    {Dec. 2014 - Present} % Date(s)
    {
      \vspace{6mm}
      {Education technology company building a real-time platform for in lecture student engagement.}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built RESTful APIs and scalable backend features using Python Django, MySQL, RabbitMQ, and Memcached.}
        \item {Developed large and interactive single-page web app using ReactJS/Flux, ES6, and SASS}
        \item {Implemented integrations with 3rd party education management platforms, securing company's largest ever enterprise contract.}
        \item {Lead efforts to implement user accessibility in the TopHat web app.}
        \item {Automated AWS Infrastructure using Ansible.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Qualcomm Inc} % Organization
	{Embedded \& Linux OS Software Engineer} % Job title
    {Toronto ON, Canada} % Location
    {May 2012 - Nov. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and developed Linux Kernel device drivers for video capture and processing on Android devices. Managed concurrency, real-time performance, security, and power efficiency. Driver launched on Samsung Galaxy Note 4.}
        \item {Developed driver and firmware for a SPI fingerprint sensor on a wearable device using STM32 micro-controller.}
        \item {Brought up new hardware components on new Qualcomm SoC using Linux device tree. Starting from  pre-silicon simulation platforms to OEM integration and commercial release.}
        \item {Bit exact simulation of a next-gen display processor for new SoC using C++.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {VerifEye Technologies Inc} % Organization
    {Audio Systems Engineering Intern} % Job title
    {Markham ON, Canada} % Location
    {Aug. 2010 - Dec. 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented a framework for objective Audio quality testing. Includes DSP based audio distortion detection in Matlab, and a python based system for blind A/B human listening tests with statistical analysis.}
      \end{cvitems}
    }
	
%---------------------------------------------------------
  \cventry
    {Vale Inco} % Organization
    {Software Engineering Intern} % Job title
    {Sudbury ON, Canada} % Location
    {May. 2009 - Aug. 2009} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented a multi-threaded Win32 application for data-logging and real-time processing, including DSP filters and Fourier transforms. Includes a .NET based monitoring GUI.}
        \item {Implemented a program on embedded Linux that interfaces with sensors and actuators, and communicates with the Win32 program over a custom TCP-based protocol.}
      \end{cvitems}
    }

%---------------------------------------------------------

\vspace{5mm}

\end{cventries}
